### 2016-10-30 paper/evaluation.tex
Updated subject section

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study. For each project, we detected the build manager
system based on the files located in the root directory (\eg,
\emph{pom.xml}) from the project in the following precedence: Maven,
Gradle, and Ant. From the 1.000 downloaded projects, we automatically
detected the build system from 806 subjects and selected the \Fix{154}
projects that we were able to compile.

>>>>

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study.\Jbc{Subject selection is currently OK but I will
use another way (eg Google BigQuery) to have access to more subjects.} To
scale the study, we considered only Maven projects with a
\emph{pom.xml} file located in the project's root directory. We could
also include support to other popular build manager systems but we
noticed that they are commonly related to a particular platform (\eg,
Gradle and Android) or the build process is based on user-defined
tasks (\eg, Ant).  \Comment{For each project, we detected the build
manager system based on the files located in the root directory (\eg,
\emph{pom.xml}) from the project in the following precedence: Maven,
Gradle, and Ant.} From the 1.000 downloaded projects, we selected the
154 projects that we were able to compile. \Jbc{Remember to update
those numbers (download + projects) after updating the subject
selection approach.}
